---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  message = FALSE,
  error = FALSE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

# FacileBiocData

<!-- 
badges: start
checkout https://lazappi.github.io/clustree/ package for some badge-inspiration

[![Travis build status](https://travis-ci.org/facilebio/FacileBiocData.svg?branch=master)](https://travis-ci.org/facilebio/FacileBiocData)
[![Codecov test coverage](https://codecov.io/gh/facilebio/FacileBioc/branch/master/graph/badge.svg)](https://codecov.io/gh/facilebio/FacileBiocData?branch=master)

badges: end -->

[![Project Status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Lifecycle: Experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

**NOTE**: This package is being actively developed and not yet feature complete.

The `FacileBiocData` package enables the use of Bioconductor-standard  data
containers, like a `SummarizedExperiment`, `DGEList`, `DESeqDataSet`, etc. as
"first-class" data-providers within the facile ecosystem.

## Example Usage

The user simply needs to call the `facilitate` function on their data container
in order to enable its use in the facile ecosystem.

```{r data-init, message=FALSE, warning=FALSE}
library(FacileBiocData)
y <- example_bioc_data("DGEList") # Materialize an edgeR::DGEList
yf <- facilitate(y)               # wrap it for facile exploration
```

We can now use `yf` within the facile framework, ie. we can analyze it using
the [FacileAnalysis][] package:

```{r, eval=FALSE}
library(FacileAnalysis)
dge.facile <- yf %>% 
  flm_def(group = "sample_type", numer = "tumor", denom = "normal") %>% 
  fdge(method = "edgeR-qlf")
```

```{r eval=FALSE}
shine(dge.facile)
```

The "facilitated" DGEList can still be used as a normal DGEList, so that you
never have to leave the standard bioconductor ecosystem:

```{r, eval=FALSE}
library(edgeR)
genes <- features(dge.facile)$feature_id # restrict to genes used in fdge()
yf <- calcNormFactors(yf[genes,,keep.lib.sizes = FALSE])
yf <- estimateDisp(yf, model.matrix(~ sample_type, data = yf$samples))
fit <- glmQLFit(yf, yf$design, robust = TRUE)
results <- glmQLFTest(fit, coef = "sample_typetumor")
dge.standard <- topTags(results, n = Inf, sort.by = "none")
```

And these two results are equivalent

```{r, eval=FALSE}
all.equal(tidy(dge.facile)$logFC, dge.standard$logFC)
```


[FacileAnalysis]: https://facilebio.github.io/FacileAnalysis/

